Forecasting the 2024 U.S. Presidential Election: Kamala Harris' Projected Victory

### 2024-11-04 paper/paper.qmd
committing changes to paper.qmd for formatting purposes

#### End Date {#sec-end-date}
End date (**'end_date'**) marks the conclusion of data collection for each poll, serving as a predictive variable in our analysis of changes in voter support over time. This inclusion helps identify patterns as Election Day approaches, potentially reflecting the impact of campaign events, debates, or political developments.
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-end-date-distribution
#| fig-cap: "Distribution of Polling End Dates. This histogram displays the frequency of polling end dates for key battleground states, highlighting peaks in polling activity around late September."

@@

```
@fig-end-date-distribution shows polling end dates from July 2024 to October 2024, with the earliest date set to July 2024, coinciding with Kamala Harris's official presidential campaign announcement on July 21, 2024. The latest end date, October 14, 2024, reflects the last data update from Project 538 [@FiveThirtyEight] on October 15, 2024. The distribution reveals that polling activity is not evenly spread, with notable peaks in early September, late September, and early October, likely corresponding to periods of heightened political interest or significant campaign events that drive increased polling activity.

>>>>

#### End Date {#sec-end-date}
End date (**'end_date'**) marks the conclusion of data collection for each poll, serving as a predictive variable in our analysis of changes in voter support over time. This inclusion helps identify patterns as Election Day approaches, potentially reflecting the impact of campaign events, debates, or political developments. @fig-end-date-distribution shows polling end dates from July 2024 to October 2024, with the earliest date set to July 2024, coinciding with Kamala Harris's official presidential campaign announcement on July 21, 2024. The latest end date, October 14, 2024, reflects the last data update from Project 538 [@FiveThirtyEight] on October 15, 2024. The distribution reveals that polling activity is not evenly spread, with notable peaks in early September, late September, and early October, likely corresponding to periods of heightened political interest or significant campaign events that drive increased polling activity.
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-end-date-distribution
#| fig-cap: "Distribution of Polling End Dates. This histogram displays the frequency of polling end dates for key battleground states, highlighting peaks in polling activity around late September."

@@

```
